Most of us who watched Knight Rider as a kid expected that by 2015 we would be driving self-aware cars like KITT - cars that would drive us without problems from point A to point B while entertaining us. However we can resort to that this is only partially true, we have successful tries at completely autonomous cars(e.g Google’s car) but for ordinary costumer they are not available. What is available is connected cars. Connected cars provide the possibility of internet-based transfer of information. This can be obtained either with embedded devices in car or smartphone. Multiple car manufacturers sell connected cars where different OEM(Original Equipment Manufacturer) devices or applications. These OEMs offer various services which are provided to you when you purchase their car, but there is a small problem. If you are not satisfied with services provided by your manafacturer, the only option you have is to buy someone else product which comes with predefined services. You can not configrue them to the extent as smartphones have apps. It is either you will get used to your OEM solution or go and buy whole solution from somebody else, nothing else. It is like we are stuck in the 90, where software offered to you had come on this particular hardware and you could not choose otherwise. It is 2015 where you can obtain music,movies,applications from various sources that does not limit you to specific hardware, so why on earth we should accept solutions offered by car manufacturers? Imagine you would buy smartphone with predifined set of applications and you could not change them or add new. Today in connected cars what is missing is operating system which would allow costumers to configure their Info-attainment system.So in my thesis I would like to solve problem where when you have car which has no connection or has connection with software you do not like, you could follow my thesis to gain insight into how to connect car and what possible services you can obtain for yourself. In first chapter I will establish some common ground on which we can build foundations of this thesis. Next we can describe the specification of problem which we need to solve and after that show implementation methods and solution to this given task.