\section{Requirements}

\subsection{Hardware}
Create a device which will be able to communicate over the Internet. Figure out how to connect this device to the OBD-II service port in vehicle. Your device will need to know position of the vehicle, create a solution wich will utilize GPS connection when available. Prepare atleast one more source of information which will be relevant for you application solution.
\subsection{Server}
Develop a software server which will be able to log and store data collected from various inputs. These inputs will be modular, your solution have to be configurable for new input sources. One of these sources will be an OBD-II port in vehicle. Figure out how to connect your device to the OBD-II service port and how to collect information from this port. Parse collected data and create database of available information. To access this database create API/REST architecture which will be accessible securely from the Internet. Use any technology available to you.
\subsection{Application}
Create an application which will utilize information collected from connected vehilce. The application needs to preform logic deduction from accessed data and act upon it. First application will  be accident detection/prevention. This application will access statistical database of accidents, look up how many of accidents happened in the location where vehicle is, if this number is higher than average inform driver of hazardous area. Design a system which will detect if accident happend, if so send an SMS/email to recepient depending on the settings, with contact information of driver and car's location. Second application will create statistical map of cars running on low fuel, so after you detect low fuel in the vehicle, log its position in your application, interpolate your collected data to the map also display real time position of cars which has low fuel.

%Solution
\subsection{Output}


