\chapter{Automatic Hardware Specification} % (fold)
\label{sec:automatic_hardware_specification}

% chapter automatic_hardware_specification (end)
\begin{itemize}
\item OBD-II (conforms to J1962 standard), works with most cars since ’96
\item Weight and Dimensions: 1.65 x 1.96 x 0.78in (42 x 50 x 20mm) 0.84oz (23.75g)
\item Temperature Tolerance: Operating: -40 \ensuremath{^\circ}F (-40 \ensuremath{^\circ}C) to 158 \ensuremath{^\circ}F (70 \ensuremath{^\circ}C), Resting: -40 \ensuremath{^\circ}F (-40 \ensuremath{^\circ}C) to 185 \ensuremath{^\circ}F (85 \ensuremath{^\circ}C)
\item Wireless: Bluetooth 4.0 Dual Mode (EDR and BLE), Made for iPhone (MFi) Certified
\item Accelerometer: Frequency: 100Hz, Precision: 0.012G
\item Security: Wireless encryption: 128-bit AES, Signed binary enforcement: 1024-bit RSA
\item Built-in GPS: GNSS engine for GPS/QZSS, Logs trip routes with no phone present
\item Audio Capabilities: Volume: 80db at 10cm at 2.5kHz
\item Firmware: Over-the-air updates via smartphone
\end{itemize}
\chapter{VI Monitor abilities} % (fold)
\label{sec:vi_monitor_abilities}
\begin{itemize}
\item Monitor parameters such as RPM, Speed, Throttle Position, Intake Manifold Pressure, Water Temperature,
Air Fuel Ratios (lambda), Air Flow Rate, Ignition Advance Fuel Pressure, and many more.
\item Perform braking and acceleration tests such as 0-60, 1/4 mile and 0-60-0 to measure your car's true 
performance. Most tests can be G-triggered for unparalleled accuracy. Each test is recorded for future comparison.
\item Avoid putting points on your license with adjustable speed warnings. Use the RPM warnings in conjunction with the adjustable Shift Light feature to get the most from your engines performance.
\item Highly accurate G-Sensor with built-in damping monitors acceleration, braking and cornering G-Forces. Also records maximum G-readings.
\item Record over 500 hours of engine and performance data on any parameters for review. Then upload the data to your computer for comparison. Ideal for measuring the effectiveness of modifications and recording drivers performance.
\item Got a Engine Warning Light, but dont know why? - VI gives you the fault code number and a description of the problem, giving you more information to take to your garage or tuner.
\item Simple stop/start timing feature allows you to record your times for later comparison on a computer.
\item VI allows you to reset fault codes yourself, It also maintains a complete MIL stats history, including time and distance since the engine warning light was activated or rest.
\item Using a Built-in Virtual Dynamomter, VI can test your vehicles true net horsepower in real world conditions.
\end{itemize}
\chapter*{Bluetooth / WiFi Combination USB Technical Details} % (fold)
\label{sec:bluetooth_wifi_combination_usb_technical_details}
\begin{itemize}
    \item Ralink RT5370L WiFi adapter + BCM2046B1 Bluetooth 3.0 adapter
    \item Full-speed Bluetooth operation with Picone and Scatternet support
    \item Compliant with Bluetooth 2.1 + EDR and Bluetooth V3.0 + HS
    \item Support for WLAN + Bluetooth coexistence for optimized performance
    \item IEEE 802.11b/g/n compliance
    \item 150 Mbps Tx (transmit) PHY data rate
    \item 150 Mbps Rx (transmit) PHY data rate
    \item USB 1.1/2.0 compliant
\end{itemize}
% chapter bluetooth_wifi_combination_usb_technical_details (end)
% chapter vi_monitor_abilities (end)
\chapter{npm packages} % (fold)
\label{sec:npm_packages}
For clarification which packages I used during implementation, with short reasoning why I used it.
\begin{itemize}
	\item \textbf{amqplib} -- library used for making amqp 0.9.1 clients for Node.js, it has been used to create client for RabbitMQ module[\ref{ssub:rabbitmq_module}]
   	\item \textbf{body-parser} -- body parsing middleware, once internal part of express, now must be installed separately, middleware is used to handle POST requests
    \item \textbf{duplexer2} -- library for creating writable and readable streams as one, used in internal structures of Data Logger.
    \item \textbf{express} -- web application framework that provides a robust set of features for web and mobile applications.
	\item \textbf{express-session} -- simple session middleware for Express, used in web-server middleware.
	\item \textbf{gps} -- GPS.js is an extensible parser for NMEA sentences, used by GPS module to parse incoming data.[\ref{ssub:gps_module}]
    \item \textbf{i2c-bus} -- I2C serial bus access used in accelerometer module[\ref{ssub:accelerometer_module}]
    \item \textbf{lodash} -- A modern JavaScript functional utility library delivering modularity, performance and extras. Library is used throughout whole application for correct handling with objects and arrays.
    \item \textbf{morgan} -- HTTP request logger middleware for node.js, used to log HTTP requests on the express server.
    \item \textbf{node-sass-middleware} -- Connect middleware for node-sass, recompile .scss or .sass files automatically for connect and express based HTTP servers.[citation needed]
    \item \textbf{object-sizeof} -- library for computing size of a JavaScript object in bytes, used in bulk module to evaluate message size[\ref{ssub:bulk_module}]
    \item \textbf{path} -- this module contains utilities for handling and transforming file paths.[https://nodejs.org/docs/latest/api/path.html]
    \item \textbf{redis} -- this is a complete and feature rich Redis client for node.js.[https://www.npmjs.com/package/redis] It is used in redis module[\ref{ssub:redis_module}]
    \item \textbf{request} -- Request is designed to be the simplest way possible to make HTTP calls. Used in IFTTT module to generate POST requests to the Maker channel[\ref{ssub:ifttt_module}]
    \item \textbf{serialport} -- Node.js library to access serial ports, used in every module which required access to serial port.
    \item \textbf{socket.io} -- node.js real-time framework server, used to communicate through web-sockets or JSON long polling
    \item \textbf{swig} -- A simple, powerful, and extendable JavaScript Template Engine. Used in HTML templates for web application.[\ref{ssub:web_application}][http://paularmstrong.github.io/swig/docs/]
\end{itemize}
% subchapter npm_packages (end)


\chapter{Resources} % (fold)
\label{sec:resources}
% chapter resources (end)
CD which contains:
\begin{itemize}
\item Digital copy of this bachelor thesis
\item All sources files
\item All configuration files which are used in this bachelor thesis
\end{itemize}
Resources which are on CD are also available on GitHub repository \url{https://github.com/dejwoo/bachelor_thesis}.