In this chapter we summarize what was achieved in our solution and compare it to the requirements and then suggests what can be done in future work with this bachelor thesis.
\section{Result} % (fold)
\label{sec:result}
We provided an embedded device running Arch Linux operating system. All peripheral devices were successfully connected to the device and are operating. Accelerometed data are recored through \gls{i2c} protocol, cellular modem is capable of connecting to the internet and sending SMS messages, Wi-Fi extension dongle is automaticaly used to create Software Access Point to which anybody with password can connect. \gls{obd} port is interconnected with device throug ELM-USB cable and is properly configured through our application to connect to the car.\\\\
An application was developed which allows collecting of data from multiple sources. Application is configurable, modular and modules are interchangeable. Internal communication between modules is designed so modules can send and accpet data. In routes modules are selectable by types, which allows to define large dataflows with simple routing. Modules are provided for gathering sensoric data from accelerometer, OBD-II port of vehicle, NMEA data from GPS sensor and time from OS. Modules for sending data are: sending SMS messages, sending messages over AMQP protocol triggering IFTTT events, storing data into Redis database and displaying data to the standard output of Node.js application. By combing these low-level modules and adding logic high-level modules are built. Modules which we developed are for reporting accidents with SMS messages, advising drivers when to shift gears based on Revolutions per Minute(RPM) of the car, sending data in bulk mode over cellular network instead of constant stream. Routes for correct functionality of the application are also provided.\\\\
Web application is accessible through wireless access point and is used for configuring modules and displaying real-time data from modules. Applicaton uopn correct instalation on embedded device works and is capable of monitoring various inputs. This information is collected, distributed and made available for different services.\\\\
% section result (end)
\section{Future work} % (fold)
\label{sec:future_work}
Main goal of future work is to make available our Data-Logger framework for everyone, i.e. create an installation module in the npm.js module directory. After Data-Logger is available, start producing application modules for various sensors, devices and services based on popular demand. Create a guide or wiki pages for better understanding of how Data-Logger works and to attract additional developers to extend it. Provide fail-safe mechanism for declaring multiple modules with same identification name to handle this error.\\\\
In modules there are even more possibilities what could be done so we name a few. RabbitMQ module should be implemented with SSL/TLS encryption to ensure data privacy when sending messages to server on the Internet. Implement additional modules to gather data from all sensors on Adafruit 10DOF breakout board as this thesis implements module for accelerometer sensor. Design more high-level modules for buisness logic.
Main application could be password protected as are consumer-grade routers, API provided by server should have authentification method, so no sensitive information can be obtained without authorization. Create an infrastruture for analyzing data gathered by developed device, with aspect of Big Data in mind. Infrastructure should be scaleable, secure and provide direct means for analyzing contents of gathered information. And lastly as infrastructure would be meaningless if there would not be enough connected cars, research how to make embedded device smaller and cheaper which would allow manufacturing on larger scale.
% section future_work (end)